---
title: Scatterplots
author: Jeremy Dahl
date: '2017-12-12'
slug: scatterplots
categories:
  - R
tags:
  - data visualization
  - scatterplot
---

Using the Lahman database, we're going to look at homerun and strikeout statistics to make a scatterplot!

The first thing we do is download the libraries needed so we can get our data and the tools necessary to visualize this data.

```{r warning=FALSE,message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

Then, we begin specifying exactly what we're looking for. With this problem, we're taking a look at players who managed to hit more than 400 homeruns and the amount of strikeouts they had.

```{r}
query<-"SELECT playerID,sum(HR),sum(SO)
FROM Batting 
GROUP BY playerID
HAVING sum(HR)>400"
sqldf(query)
```

Now that we have the information, we will begin to visualize this data.

```{r}
query<-"SELECT playerID,sum(HR) AS CareerHR,sum(SO) AS CareerSO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>400"
result<-sqldf(query)
```

Homeruns will be on the y-axis and strikeouts will be on the x-axis and a title is added as well. 

```{r}
ggplot()+
geom_point(data=result,aes(x=CareerSO,y=CareerHR),size=3)+
ggtitle("Career Strikeouts and Homeruns")+
xlab("Career Strikeouts")+
ylab("Career Homeruns")
```

Using ggplot2, we were able to create this beautiful graph displaying data from all-time greats in MLB, so cheers to that!

See ya next time!