---
title: SQL
author: Jeremy Dahl
date: '2017-10-01'
slug: sql
categories:
  - R
tags:
  - SQL
---

SQL
Filtering Rows and Columns

With SQL, you can filter columns with SELECT and rows with WHERE. Let's look at an example using the Lahman baseball database.First we need to load some packages.

```{r message=FALSE,warning=FALSE}
library(Lahman)
library(sqldf)
```

Suppose we want to see the homerun totals for the 1927 Yankees. We could write the following:

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='NYA'and yearID=1927"
sqldf(query)
```

In this scenario, we can filter our selection to players from the New York Yankees who have had seasons of 40 or more home runs while striking out less than 60 times, which is quite a feat.

```{r}
query<-"SELECT playerID,teamID,yearID,HR FROM Batting
WHERE teamID='NYA' and HR>=40 and SO<60"
sqldf(query)
```

If we want to broaden the search, we can select players from any team who had more than 40 home runs and less than 60 strikeouts.

```{r}
query<-"SELECT playerID,teamID,yearID,HR,SO FROM Batting
WHERE HR>40 and SO<60"
sqldf(query)
```

As you can see with the data below, we can even narrow it down to Philadelphia Phillies in the 1970s who had more than 30 home runs in a season.

```{r}
query<-"SELECT playerID,teamID,yearID,HR FROM Batting
WHERE teamID='PHI' and HR>30 and yearID<=1979 and yearID>=1970"
sqldf(query)
```

