---
title: Time Series
author: Jeremy Dahl
date: '2017-12-12'
slug: time-series
categories:
  - R
tags:
  - SQL
  - data visualization
  - time series
---

Just like last time, we will be taking a look at data visualization! Thankfully, this time we will be focusing on perhaps the best baseball player of all time on the best team of all time: Babe Ruth of the New York Yankees! (Unfortunately we'll have to include his statistics as a member of the Red Sox, but we'll have to look over that)

The time series will give us an opportunity to see how his statistics progressed over his career. 

```{r warning=FALSE,message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

To look at Babe Ruth’s homeruns over his twenty-two seasons, we use this sql request: 

```{r}
query<-"SELECT yearID,HR FROM Batting WHERE playerID='ruthba01'"
result<-sqldf(query)
```

Next, it is time for the visualization! The time series is similar to the scatterplot, except with this we'll be able to see a line that will connect the points together that will help identify the progress over time!

```{r}
ggplot()+
  geom_point(data=result,aes(x=yearID,y=HR),size=1/2)+
  geom_line(data=result,aes(x=yearID,y=HR))+
  ggtitle("Babe Ruth's, aka The GOAT, Homeruns by Year")+
  xlab("Year")+
  ylab("Number of Homeruns")
```

It's always a fun time to look into the past at Yankees legends, so hopefully you'll join me again and hopefully we'll be able to take another look into the New York Yankees! 